---
title: "Stock Prices"
author: "Trenton Pulsipher"
date: "10/15/2018"
output: html_document
---

```{r setup, error = F, message = F, warning = F}

knitr::opts_chunk$set(echo = FALSE)

library(shiny)
library(Quandl)
  Quandl.api_key("1xrGSwDRn_MapbqUyt2x") # my personal free key
library(tidyverse)
library(lubridate)
library(rbokeh)

  ## Grab All Tickers available for free from Quandl
# allTickers <- system('curl "https://www.quandl.com/api/v3/databases/WIKI/codes?api_key=1xrGSwDRn_MapbqUyt2x"', inter = T)
allTickers <- read_csv("secwiki_tickers.csv") %>%
  filter(str_detect(Price, "WIKI"))

```


```{r functions, error = F, message = F, warning = F}

# function to grab the data from Quandl
get_raw_data <- function(ticker) {
  # reminder: my Quandl API_key is hard coded below
  url <- paste0("https://www.quandl.com/api/v3/datasets/WIKI/", ticker, "/data.csv?collapse=daily&column_index=4&api_key=1xrGSwDRn_MapbqUyt2x")
  system(paste0('curl ', url), intern = T)
}

```


#### Data

##### Quandl
Quandl provides access to data for financial modelers. One data source, [WIKI](https://www.quandl.com/databases/WIKIP), is free and represents "End of day stock prices, dividends and splits for 3,000 US companies, curated by the Quandl community and released into the public domain."


#### Analysis

##### Time-Series

```{r functions, error = F, message = F, warning = F}
allTickers %>% 
  filter(Ticker == input$ticker) %>%
  select(Name, Sector, Industry))


# grab the raw data from Quandl
get_raw_data(input$ticker) %>%
  as.tibble() %>%
  slice(-1) %>% # remove the header line
  mutate(Date = ymd(unlist(lapply(str_split(value, ","), "[[", 1))),
         Close = as.numeric(unlist(lapply(str_split(value, ","), "[[", 5)))) %>%
  figure(xlab = "", ylab = "Price at Closing (Daily)") %>%
    ly_points(Date, Close, hover = list("Date" = Date, "Closing Price" = Close))


## NOTES:
# https://www.quandl.com/databases/WIKIP
# DESCRIPTION of WIKI data: End of day stock prices, dividends and splits for 3,000 US companies, curated by the Quandl community and released into the public domain.
# could vary more than just closing price
# could provide shorter window (say last year) if desired

